\sysfull

### 2018-08-06 paper/asplos19/intro.tex
intro

\item[C1] \emph{Overcoming Task Transition Overhead:} given unpredictable incoming energy, how to save computation progress, i.e. saving state at task transitions, as rare as possible? \sys tries to minimize task transition overhead by estimating energy conditions at run-time using \emph{recent execution history} as a metric.

\item[C2] \emph{Dynamic Memory Consistency Handling:} merging static tasks on the fly gives rises  the need for dynamic memory consistency handling. This leads to the second challenge: how to dynamically detect inter-task data dependencies and ensure efficient protection against power interrupts? \sys addresses this challenge by using a novel approach called \emph{dynamic group privatization}---performing real-time dependency tracking to enable protection on a task transition. Individual variables tracking, however, slows down a system dramatically. Therefore, \sys protects global variables in a batch. Moreover, it optimizes data transfers by using Direct Memory Access (DMA).

>>>>

\item[C1] \emph{Overcoming Task Transition Overhead:} given unpredictable incoming energy, how to save computation state at task transitions as rare as possible? \sys tries to minimize task transition overhead by estimating energy conditions at run-time using \emph{recent execution history} as a metric.

\item[C2] \emph{Dynamic Memory Consistency Handling:} merging static tasks on the fly gives rises  the need for dynamic memory consistency handling. This leads to the second challenge: how to dynamically detect inter-task data dependencies and ensure efficient protection against power interrupts? \sys addresses this challenge by using a novel approach called \emph{dynamic group privatization}---performing real-time dependency tracking to enable protection on a task transition. Individual variables tracking, however, slows down a system dramatically. Therefore, \sys keeps memory consistent through \emph{memory virtualization} optimized for bulk accesses to task-shared data with high locality.

%Therefore, \sys protects global variables in a batch. Moreover, it optimizes data transfers by using Direct Memory Access (DMA).
